Experiments with Real-World Data

### 2022-07-24 dev/notebooks/real_world.qmd
final streamlining and now running for credit data

## Models

```{julia}
# Models:
model = Models.build_mlp()
λ = 0.1
model_laplace = Laplace(model, λ=λ)
M = FluxModel(model)
M_laplace = LaplaceReduxModel(model_laplace)
models = Dict(:laplace=>M_laplace, :mlp=>M)
```

## Generators

>>>>

```{julia}
catalogue = AlgorithmicRecourseDynamics.Data.load_real_world()
choices = [:german_credit_numerical, :give_me_some_credit_balanced]
data_sets = filter(p -> p[1] in choices, catalogue)
```

```{julia}
models = [:FluxModel, :LaplaceReduxModel]
generators = Dict(
    :Greedy=>GreedyGenerator(), 
    :Generic=>GenericGenerator(),
    :REVISE=>REVISEGenerator(),
    :DICE=>DiCEGenerator()
)
```

```{julia}
run_experiments(data_sets,models,generators)
```
